---
title: "EGU short course: Communicating data quality through open reproducible research"
author: 
- affiliation:  "52°North Spatial Information Research GmbH"
  name: "Markus Konkol"
- affiliation:  "52°North Spatial Information Research GmbH"
  name: "Simon Jirka"
date: "2023-04-25"
licenses:
  code: Apache License 2.0
  data: CC0
  text: CC-BY-4.0
output: html_document
abstract: "This R Markdown files creates a simple IDW interpolation based on an artificial dataset."
params:
  checked: FALSE
  accuracy: 0.2
  idwPower: 2.0
  adjusted: null  
bibliography: references.bib
---

```{r setup, include=FALSE}
#Some global parameters for the chunks in this Rmd. Other options: include, warning, message
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
#sessionInfo()
```

Import libraries and source code scripts. Outsourcing code snippets to some R files allows to keep the R Markdown file light.
```{r importLibraries, echo = FALSE}
library(tmap)
library(sp)
library(RColorBrewer)
library(gstat)
library(raster)
library(geojsonio)

source("code/functions.R")
source("code/plotFunctions.R")
```

tmap by @tmap

sp by @sp

RColorBrewer by @rcb

gstat by @gstat

raster by @raster

geojsonio by @gjio

Import dataset.
```{r importData}
temperature_values <- read.csv(file="data/temperature_values.csv", sep = ';', header = TRUE)
```

Filter dataset according to parameters in YAML. Here, "checked" indicates that a sensor which made an observation was checked and calibrated. 

```{r filterData}
param <- params$checked
if (params$checked) {
  temperature_values <- dplyr::filter(temperature_values, temperature_values$quality_level == "checked")  
}

temperature_values <- dplyr::filter(temperature_values, temperature_values$accuracy < params$accuracy)
params$adjusted
```

Create _SpatialPointsDataFrame_
```{r createSPDF}
coord_ref_sys <- CRS("+init=epsg:4326 +proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
points_spdf <- createSpatialPointsDataFrame(temperature_values$longitude, 
                                          temperature_values$latitude, 
                                          temperature_values, 
                                          coord_ref_sys)
```

Create _SpatialPolygonsDataFrame_
```{r createSPolyDF}
lake <- geojson_read("data/lake_aasee.geojson")
lake_spolydf <- createSpatialPolygonsDataFrame(lake, coord_ref_sys)
```

Align the bounding boxes of the observations and the study area.
```{r alignBBX}
points_spdf@bbox <- lake_spolydf@bbox
```

Plot study area
```{r studyArea, results = 'hide'}
studyarea <- plotStudyArea(lake_spolydf, points_spdf)
studyarea

jpeg("figures/studyarea.jpg")
studyarea
dev.off()
```

Run and plot interpolation
```{r interpolate}
points_spdf.idw <- runInterpolation(points_spdf, temperature_values$measurement, params$idwPower)

raster_object       <- raster(points_spdf.idw)
raster_object.mask  <- mask(raster_object, lake_spolydf)

idw <- plotInterpolationMap(raster_object.mask, points_spdf)
idw

jpeg("figures/idw.jpg")
idw
dev.off()
```
Create a IDW map with temperature variation measurements coming from the normal distribution using the accuracy as a standard deviation. Every run will result in a different map. However, potentially very small changes should be visible.
```{r uncertainty}
sample = generateAccuracyValues(points_spdf$measurement)
points_spdf$var1 <- sample[,1]
points_spdf$var2 <- sample[,2]
points_spdf$var3 <- sample[,3]
points_spdf$var4 <- sample[,4]
points_spdf$var5 <- sample[,5]
points_spdf$var6 <- sample[,6]
points_spdf$var7 <- sample[,7]
points_spdf$var8 <- sample[,8]
points_spdf$var9 <- sample[,9]
points_spdf$var10 <- sample[,10]
#print(cbind(points_spdf$var1, points_spdf$var2, points_spdf$var3, points_spdf$var4, 
#            points_spdf$var5, points_spdf$var6, points_spdf$var7, points_spdf$var8,
#            points_spdf$var9, points_spdf$var10))

points_spdf.idw_var1 <- runInterpolation(points_spdf, points_spdf$var4, params$idwPower)

raster_object_var1       <- raster(points_spdf.idw_var1)
raster_object.mask_var1  <- mask(raster_object_var1, lake_spolydf)

idw_var1 <- plotInterpolationMap(raster_object.mask_var1, points_spdf)
idw_var1

jpeg("figures/idw_var1.jpg")
idw_var1
dev.off()

```


## References