---
title: "EGU short course: Communicating data quality through open reproducible research"
author: 
- affiliation:  "52°North Spatial Information Research GmbH"
  name: "Markus Konkol"
- affiliation:  "52°North Spatial Information Research GmbH"
  name: "Simon Jirka"
date: "2023-04-25"
licenses:
  code: MIT License
  data: CC0
  text: CC-BY-4.0
output: html_document
abstract: "This R Markdown files creates a simple IDW interpolation based on an artificial dataset."
params:
  quality_level: FALSE #FALSE: checked/unchecked values considered, TRUE: only checked values considered. 
  accuracy: 0.2 #only values from sensors with an accuracy smaller/equal to 0.2 considered.
  idwPower: 2.0 #IDW interpolation power.
  data_processing: FALSE #FALSE: adjusted/raw values considered, TRUE: only adjusted values considered.  
bibliography: references.bib
---

```{r setup, include=FALSE}
#Some global parameters for the chunks in this Rmd. Other options: include, warning, message
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
#sessionInfo()
```

Import libraries and source code scripts. Outsourcing code snippets to some R files allows to keep the R Markdown file light.
```{r importLibraries, echo = FALSE}
library(tmap)
library(sp)
library(RColorBrewer)
library(gstat)
library(raster)
library(geojsonio)

source("code/functions.R")
source("code/plotFunctions.R")
```

tmap by @tmap

sp by @sp

RColorBrewer by @rcb

gstat by @gstat

raster by @raster

geojsonio by @gjio

Import dataset.
```{r importData}
temperature_values <- read.csv(file="data/temperature_values.csv", sep = ';', header = TRUE)
```

Filter dataset according to parameters in YAML. Here, "checked" indicates that a sensor which made an observation was checked and calibrated. 

```{r filterData}
if (params$quality_level) {
  temperature_values <- dplyr::filter(temperature_values, temperature_values$quality_level == "checked")  
}

temperature_values <- dplyr::filter(temperature_values, temperature_values$accuracy < params$accuracy)
```

Create _SpatialPointsDataFrame_
```{r createSPDF}
coord_ref_sys <- CRS("+init=epsg:4326 +proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs")
points_spdf <- createSpatialPointsDataFrame(temperature_values$longitude, 
                                          temperature_values$latitude, 
                                          temperature_values, 
                                          coord_ref_sys)
```

Create _SpatialPolygonsDataFrame_
```{r createSPolyDF}
lake <- geojson_read("data/lake_aasee.geojson")
lake_spolydf <- createSpatialPolygonsDataFrame(lake, coord_ref_sys)
```

Align the bounding boxes of the observations and the study area.
```{r alignBBX}
points_spdf@bbox <- lake_spolydf@bbox
```

Plot study area
```{r studyArea, results = 'hide'}
studyarea <- plotStudyArea(lake_spolydf, points_spdf)
studyarea

png("figures/studyarea.png")
studyarea
dev.off()
```

Run and plot interpolation
```{r interpolate}
points_spdf.idw <- runInterpolation(points_spdf, temperature_values$measurement, params$idwPower)

raster_object       <- raster(points_spdf.idw)
raster_object.mask  <- mask(raster_object, lake_spolydf)

idw <- plotInterpolationMap(raster_object.mask, points_spdf)
idw

png("figures/idw.png")
idw
dev.off()
```
Create a IDW map with temperature variation measurements coming from the normal distribution using the accuracy as a standard deviation. Every run will result in a different set of maps in the figures folder. The maps will differ only slightly.
```{r uncertainty}
sample = generateAccuracyValues(points_spdf$measurement)
measurement_variations_columns <- paste("points_spdf$var", 1:10, sep="")
sample_supset <- paste("sample[,",1:10,"]", sep="")
mergeCol <- paste(paste(measurement_variations_columns, sample_supset, sep="<-"), collapse=";")
eval(parse(text=mergeCol))

interpolationVariables <- paste("points_spdf.idw_var", 1:10, sep="")
interpolationRuns <- paste("runInterpolation(points_spdf, points_spdf$var",1:10,", params$idwPower)", sep="")
merfeInterpolationVariablesRuns <- paste(paste(interpolationVariables, interpolationRuns, sep="<-"), collapse=";")
eval(parse(text=merfeInterpolationVariablesRuns))

rasterVariables <- paste("raster_object_var", 1:10, sep="")
rasterFunctions <- paste("raster(points_spdf.idw_var",1:10,")", sep="")
mergeRasterVariablesFunctions <- paste(paste(rasterVariables, rasterFunctions, sep="<-"), collapse=";")
eval(parse(text=mergeRasterVariablesFunctions))

maskVariables <- paste("raster_object.mask_var", 1:10, sep="")
maskFunctions <- paste("mask(raster_object_var",1:10,", lake_spolydf)", sep="")
mergeMaskVariablesFunctions <- paste(paste(maskVariables, maskFunctions, sep="<-"), collapse=";")
eval(parse(text=mergeMaskVariablesFunctions))

plotVariables <- paste("idw_var", 1:10, sep="")
plotFunctions <- paste("plotInterpolationMap(raster_object.mask_var",1:10,", points_spdf)", sep="")
mergePlotVariablesFunctions <- paste(paste(plotVariables, plotFunctions, sep="<-"), collapse=";")
eval(parse(text=mergePlotVariablesFunctions))

for(i in 1:10) {
  eval(parse(text = paste("png('figures/idw_var", i, ".png')", sep = "")))
  eval(parse(text = paste("print(idw_var", i, ")", sep = "")))
  dev.off()
}
```

## References